Software Ticket Quality

### 2017-11-30 proposal/mprop.tex
Change proposal lightly
Add 2 papers on software waste to proposal

\textbf{Secret Life of Bugs}\cite{aranda2009secret}:
\begin{itemize}
\item What were the goals?
  The paper tries to understand and analyze common bug fixing coordination
  activities. Another goal of the paper was to analyze the reliability of
  repositories in terms of software projects coordination and propose
  different directions on how to implement proper tools.
\item What was the method?
  They executed a field study which was split into two parts:
  \begin{itemize}
  \item firstly, they did an exploratory case study of bug repos histories;
  \item secondly, they conducted a survey with professionals (i.e.\ testers,
    developers).
  \end{itemize}
  All data and interviews were conducted using Microsoft bug repositories and
  employees.
\item What did they learn?
  They learned that there are multiple factors which influence the coordination
  activities that revolve around bug fixing, such as organizational, social and
  technical knowledge, thus one cannot infer any conclusions only by automatic
  analysis of the bug repositories. Also, through surverying the professionals,
  they reached the conclusion that there are 8 main goals which can be used for
  better tools and practices:
  \begin{itemize}
  \item probing for ownership;
  \item summit;
  \item probing for expertise;
  \item code review;
  \item triaging;
  \item rapid-fire emailing;
  \item infrequent, direct email;
  \item shotgun emails.
  \end{itemize}
\item Relevance to our work: this paper is one of the key papers for our
  research paper.
\end{itemize}

\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to show that poor estimation analysis techniques 
    in software projects will lead to wrong conclusions regarding cost 
    estimation accuracy. Moreover, they also propose a framework for 
    better analysis of software cost estimation error.
  \item \textbf{What was the method?}
    They approached a real-world company where they conducted analysis on
    their cost estimation techniques.
  \item \textbf{What did they learn?}
    They learned that regular, straight-forward types of cost estimation analysis
    techniques error lead them to wrong conclusions. 
  \item \textbf{Relevance to our work}: it showed us that we need to be careful
    when selecting techniques for cost estimation in our own research.
\end{itemize}

>>>>

Another work that is trying to analyze the waste around software coordination activities
is the one of \citet{aranda2009secret}. They are trying to understand common bug fixing
coordination activities in terms of software projects coordination and propose different
directions on how to implement proper tools. Firstly, the conducted a field study which was
split into two parts:
  \begin{itemize}
    \item led an exploratory case study of bug repositories histories;
    \item then, they conducted a survey with professionals (e.g. testers, developers).
  \end{itemize}
After they finished the 2 phases, they learned that there are multiple factors which
influence the coordination activities that revolve around bug fixing, such as organizational,
social and technical knowledge, thus one cannot infer any conclusions only by automatic analysis 
of the bug repositories. Also, through surveying the professionals, they reached the conclusion
that there are \emph{eight main goals} which can be used for better tools and practices: summit, 
probing for ownership, probing for expertise, code review, triaging, rapid-fire emailing, 
shotgun emails and infrequent/direct email.

However, having discussed about software and communication waste, what work has been done
around another major software activity, software cost estimation? The paper from 
\citet{grimstad2006framework} tried to show that poor estimation analysis techniques
in software projects will lead to wrong conclusions regarding cost estimation accuracy.
Moreover, they also propose a framework for better analysis of software cost estimation
error. They approached a real-world company where they conducted analysis on their cost
estimation techniques. Eventually, they learned that regular, straight-forward types
of cost estimation analysis techniques errors lead to wrong conclusions, thus increasing
the risk of poor coordination activities.
